---
title: ""
author: "Jonathan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: spacelab
params:
  first_inspection: first_inspection,
  last_inspection: last_inspection,
  nb_restaurants: nb_restaurants
  nb_cuisine_types: nb_cuisine_types
  rest_count_by_cuisine: rest_count_by_cuisine
  grade_count: grade_count
  a_grade_percent: a_grade_percent
  inspections_by_month_plot: inspections_by_month_plot
  fit_inspections: fit_inspections
---
  
```{r setup, include=FALSE}
pacman::p_load(DT)
pacman::p_load(htmlTable)
```

# Exploring the NYC Restaurant Inspection Results Dataset

#### Intro

The `DOHMH New York City Restaurant Inspection Results` dataset provides
information on restaurant violations and grades following city inspections. This
report includes inspections from **`r params$first_inspection`** to
**`r params$last_inspection`** from **`r params$nb_restaurants`** restaurants. 

Inspection grades of **A**, **B**, and **C** are given out based on an
inspection score. A for scores between 0 and 13, B for score between 14 and 27,
and C for scores above 28. 

---

#### Inspections per Month

##### How many inspections are carried out each month?
```{r echo=FALSE}
params$inspections_by_month_plot
```

Although inspection dates start in 2011, the majority of inspections appear
to occur from 2015 onwards. From this point onwards, the number of inspections
varies roughly between 7500 and just over 10000 each month.

##### Do there appear to be any seasonal trends?
```{r echo=FALSE}
plot(params$fit_inspections)
```

Inspections appear to increase slightly at the beginning of the year (~ February ),
and dip around the end of the year (~ November ).

---

#### Inspection Results

##### How many inspections resulted in grades A, B and C?

```{r echo=FALSE}
htmlTable::htmlTable(params$grade_count,
                     css.cell = "padding-left: 2em; padding-right: 2em;")
```

---

##### How many restaurants were inspected of each cuisine type?

```{r echo=FALSE}
datatable(params$rest_count_by_cuisine, options = list(pageLength = 6))
```



---
  
## Footnote

#### Dataset source

* https://data.cityofnewyork.us/Health/DOHMH-New-York-City-Restaurant-Inspection-Results/43nn-pn8j
